---
title: "Project 2 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Kaite Brinkers, guided with problems 2-5, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
myDF <- read.csv("/class/datamine/data/disney/metadata.csv")
head(myDF)
```

### Question 2

```{r}
our_vec <- myDF$WDWMAXTEMP
our_vec[1]
our_vec[50]
typeof(our_vec)
```

### Question 3

```{r}
first50 <- head(our_vec,n=50)
last50 <- tail(our_vec,n=50)
mymix = first50 + last50
```

### Question 4

```{r}
hot <- myDF$WDWMAXTEMP[myDF$WDWMAXTEMP>=80]
length(hot)
mymix = hot + first50
```
R sums up the vectors by recycling the elements in the shorter one until it is long enough to match it

### Question 5

```{r}
barplot(our_vec)
```

### Question 6

I like the Average temperature range because it is visually appealing and simple to understand. It gets the message across well without too many distractions. This could be improved my adding colors relating to the seasons. For example white for colder months and yellow for warmer months. One interesting observation is that there is is a space around the plot area to indicate the highs and lows range around the average temperature of eachmonth.  

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
