---
title: "Project 9 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Katie Brinkers guided with problems 1-7, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
library(imager)

books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")

get_author_name <- function(my_authors_dataset, my_author_id){
  return(my_authors_dataset[my_authors_dataset$author_id==my_author_id,'name'])
}

fun_plot <- function(my_authors_dataset, my_books_dataset, my_book_id, display_cover=T) {
  book_info <- my_books_dataset[my_books_dataset$book_id==my_book_id,]
  all_books_by_author <- my_books_dataset[my_books_dataset$author_id==book_info$author_id,]
  author_name <- get_author_name(my_authors_dataset, book_info$author_id)
  
  img <- load.image(book_info$image_url)
  
  if(display_cover){
    par(mfrow=c(1,2))
    plot(img, axes=FALSE)
  }
  
  plot(all_books_by_author$num_pages, all_books_by_author$average_rating, 
       ylim=c(0,5.1), pch=21, bg='grey80',
       xlab='Number of pages', ylab='Average rating', 
       main=paste('Books by', author_name))
  
  points(book_info$num_pages, book_info$average_rating,pch=21, bg='orange', cex=1.5)
}
fun_plot(authors, books,17332218)
fun_plot(authors, books, 157993)
```
3 Arguments are my_author_dataset, my_books_dataset, book_id
The function prints the title and plot of the books versus others by page number and average rating

### Question 2

```{r}
#Function where it also checks to see if my_book_id is within dataset, and prints "Book ID not found." if it does not exist, exiting the function

books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")

get_author_name <- function(my_authors_dataset, my_author_id){
  return(my_authors_dataset[my_authors_dataset$author_id==my_author_id,'name'])
}

fun_plot <- function(my_authors_dataset, my_books_dataset, my_book_id, display_cover=T) {
  if (0==sum(my_books_dataset$book_id==my_book_id))
  {
    stop("Book ID not found.")
  }
  book_info <- my_books_dataset[my_books_dataset$book_id==my_book_id,]
  all_books_by_author <- my_books_dataset[my_books_dataset$author_id==book_info$author_id,]
  author_name <- get_author_name(my_authors_dataset, book_info$author_id)
  
  img <- load.image(book_info$image_url)
  
  if(display_cover){
    par(mfrow=c(1,2))
    plot(img, axes=FALSE)
  }
  
  plot(all_books_by_author$num_pages, all_books_by_author$average_rating, 
       ylim=c(0,5.1), pch=21, bg='grey80',
       xlab='Number of pages', ylab='Average rating', 
       main=paste('Books by', author_name))
  
  points(book_info$num_pages, book_info$average_rating,pch=21, bg='orange', cex=1.5)
}
#fun_plot(authors, books, 123) Comments out for knitting purposes
fun_plot(authors, books, 19063)
```

### Question 3

```{r}
#Function that accepts an authors name and returns the author_id of the author
get_author_id <- function(my_authors_dataset, my_author_name)
{
  return(my_authors_dataset$author_id[my_authors_dataset$name==my_author_name])
}
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")
get_author_id(authors, "Brandon Sanderson") # 38550
get_author_id(authors, "J.K. Rowling") # 1077326
```


### Question 4

```{r}
#Function that accepts the books dataset as an argument and utilize my_books_dataset within the function
search_books_for_word <- function(word, my_books_dataset) {
  return(my_books_dataset[grepl(word, my_books_dataset$description, fixed=T),]$title)
}

search_books_for_word(" Fat Cat ",books)
```

### Question 5

```{r}
#Function that searches for title that have the specific word searched
search_title <- function(word, my_books_dataset) {
  return(my_books_dataset[grepl(word, my_books_dataset$title, fixed=T),]$title)
}

search_title(" Fat Cow ",books)
search_title(" Little Dog ",books)
```

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
