---
title: "Project 4 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Hilda Ibriga and Katie Brinkers guided with problems 1-5, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")

total <- 0
length_notna_not99 <- 0
for (i in splash_mountain$SPOSTMIN) {
  #Testing whether value in SPOSTMIN is na or -999
  if ((!is.na(i)) & (i != -999)) {
  #Updating total with values of SPOSTMIN that met conditions above
    total <- total + i
  #Counting many elements are not na or -999
  length_notna_not99 <- length_notna_not99 + 1
  }
}
total
mean = total/length_notna_not99
mean
#Number of values that are not na or -999
```
The mean posted wait time is 43.38925

### Question 2

```{r}
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")

status <- c()
for (i in 1: nrow(splash_mountain)) {
  #Takes values applies of closed to each row that does not meet its criteria
  if(any(splash_mountain[i, c("SPOSTMIN", "SACTMIN")] == -999, na.rm=T)) {
    status[i] <- "closed"
  }
  #Takes values applies of open to each row that meet its criteria
  else {
    status[i] <- "open"
    
  }
}
#Making a new column by converting status to a factor
splash_mountain$status <- factor(status)
head(splash_mountain)
head(splash_mountain$status)
table(splash_mountain$status)
str(splash_mountain)
```
The output for closed is 24326 and the open one is 199610.

### Question 3

```{r}
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")
#Creating a new column called status and assigning new values to open
splash_mountain$status <- "open"

#Change values that are open to closed if they do not meet the criteria
splash_mountain$status[which(splash_mountain$SPOSTMIN == -999 | splash_mountain$SACTMIN == -999)] <- "Closed"
#Make a new column called status
splash_mountain$status <- factor(status)
str(splash_mountain)
```

### Question 4

```{r}
#Tabulating status (table of count) then made pie function
splash_mountain_open_closed_pie_chart <- pie(table(splash_mountain$status))
```

### Question 5

```{r}
#New vector with ride names
ride_names <- c("splash_mountain", "soarin", "pirates_of_caribbean", "expedition_everest", "flight_of_passage", "rock_n_rollercoaster")
#Pasting vector and attaching .csv
ride_files <- paste0(c("/class/datamine/data/disney/"), ride_names, ".csv")
par(mfrow=c(2,3))
for (i in 1:length(ride_names)) {
  #Store files into dataframe
  ride_dataframe <- read.csv(ride_files[i])
  ride_dataframe$status <- "open"
  #Change values that are open to closed if they do not meet the criteria
  ride_dataframe$status[which(ride_dataframe$SPOSTMIN == -999 | ride_dataframe$SACTMIN == -999)] <- "Closed"
  #Make a new column called status
  ride_dataframe$status <- factor(ride_dataframe$status)
  #Made Pie function
  pie(table(ride_dataframe$status), main = ride_names[i])
}
```

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
