---
title: "Project 5 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Hilda Ibriga and Katie Brinkers guided with problems 1-5, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
#Combines accident files into one big dataset
accidents <- rbind(read.csv("/class/datamine/data/fars/1975/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1976/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1977/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1978/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1979/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1980/ACCIDENT.CSV"),
                   read.csv("/class/datamine/data/fars/1981/ACCIDENT.CSV"))
#Pasting 19 to every value in the year column
accidents$YEAR <- paste0("19", accidents$YEAR)
#Tells all unique values
unique(accidents$YEAR)
```

### Question 2

```{r}
#Printing values where statement is true, false and N/A, specifically looking for true values
table(accidents$DRUNK_DR >= 1&accidents$SCH_BUS >= 1, useNA= "always")
#The true value is 101
```

### Question 3

```{r}
#Print number of accidents involving more than 1 drunk driver 
table(accidents$YEAR[(accidents$DRUNK_DR >= 1)&(accidents$SCH_BUS >= 1)])
```
1978 had the largest number of accidents

### Question 4

```{r}
#Finds the mean number of motorists in an accident and drunk drivers
for (i in 0:6) {
  print(paste0("The mean number of motorists in an accident with ", i, " drunk drivers is ", mean(accidents$PERSONS[accidents$DRUNK_DR == i],na.rm = TRUE)))
}
#Other way to get the answer
tapply(accidents$PERSONS, accidents$DRUNK_DR, mean)
```

### Question 5

```{r}
library(RColorBrewer)
#Creating a vector of states.
sN <- c(17, 18, 26, 39)

# Extract data from accidents only where the state code is either 17, 18, 26, or 39
mwDF <- accidents[accidents$STATE %in% sN,]

t <- table(mwDF$STATE, mwDF$MONTH)

# Using a table comparing the number of accident rows in each month for each state as data for a barplot
barplot(table(mwDF$STATE, mwDF$MONTH),
        legend=rownames(t),
        xlab="Month",
        ylab="# of Accidents",
        main="Accidents for Each State, by Month",
        col=brewer.pal(4, "Set1")
)
```
The most accidents happen in month 8 followed by month 7 and month 9. This does not suprise me because this is when people are most free.

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
