---
title: "Project 1 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: N/A
## Online resources used: Dr.Ward's 2 Tutorial Videos (Start to Finish)

### Question 1

The memory on the 7 frontend nodes is 4 * 512 + 3 * 768 = 4352 GB = 4.3 TB
The memory on the 28 nodes in the sub-cluster is: 24 * 64 + 4 * 192 = 2304 GB = 2.3 TB
The memory on Kevin's laptop is 8 GB.

### Question 2

```{r}
system("hostname", intern=T)
```
I am working on Scholar front end number 0.

### Question 3

"You've successfully loaded The Data Mine R settings!"

### Question 4 

There are 3 chunks of R code, 1 chunk of bash, 1 chunk of Python, 1 chunk of SQL

### Question 5

Output displayed is: 1, 2, 3
```{r}
my_variable <- c(1,2,3)
my_variable
```

### Question 6

```{r}
4 * 512 + 3 * 768
24 * 64 + 4 * 192
```

### Question 7 

```{r}
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")
head(splash_mountain)
```

### Question 8

Submit Rmd file, original R file, and resulting pdf file.

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
