---
title: "Project 8 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Katie Brinkers guided with problems 1-7, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")

# A function that, given a string (myColumn), returns the string
# without any punctuation.
strip_punctuation <- function(myColumn) {
  # Use regular expressions to identify punctuation.
  # Replace identified punctuation with an empty string ''.
  desc_no_punc <- gsub('[[:punct:]]+', '', myColumn)
  
  # Return the result
  return(desc_no_punc)
}
books$description<- strip_punctuation(books$description)
```
The name of the function is strip puncuation. There is one argument which is named myColumn.

### Question 2

```{r}
#String split by space
test_string <- "This is  a test string  with no punctuation"
strsplit("This will be   split by space.", " ")
```
It would be not be an accurate counting because there are double spaces (two).

### Question 3

```{r}
#Use which to fix issue by unlisting strsplt result 
strsplit("This will be   split by space.", " ")
x <- unlist(strsplit(test_string, " "))
length(which(x!=""))
```


### Question 4

```{r}
# word_count is a function that accepts a sentence as an argument,
# strips punctuation and extra space, and returns the number of 
# words in the sentence.
word_count <- function(sentence) {
  # strip punctuation and save into an auxiliary variable
  aux <- gsub('[[:punct:]]+','', sentence)
  
  # split the sentence by space and remove extra spaces
  result <- sum(unlist(strsplit(aux, " ")) != "")
  return(result)
}
second <- books[2, "description"]
word_count(second)
```
There are 211 words total. 

### Question 5

```{r}
#Adds together all words and titles 
title_count <- function(name) {
  aux <- gsub('[[:punct:]]+','', name$title)
  result <- sum(unlist(strsplit(aux, " ")) != "")
  return(result)
}
title_count(books) 
```
Total number of words and titles combined

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
