---
title: "Project 3 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Hilda Ibriga, guided with problems 1-6, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
splash_mountain <- read.csv("/class/datamine/data/disney/splash_mountain.csv")
str (splash_mountain)
dim (splash_mountain)
```
There are 223,936 rows and and 4 columns in the dataset

### Question 2

```{r}
mean (splash_mountain$SPOSTMIN,na.rm=T)
sqrt (var (splash_mountain$SPOSTMIN,na.rm=T))
```
The results of running the R code is -71.70373 for the mean and 328.0586 for the standard deviation. The results do not make sense because time is negative. I am getting a negative answer because the value is indicated that the ride as being closed.

### Question 3

```{r}
mean (splash_mountain$SPOSTMIN,na.rm=T)
mean(splash_mountain$SPOSTMIN [which (splash_mountain$SPOSTMIN>-999)],na.rm=T)
sqrt (var (splash_mountain$SPOSTMIN,na.rm=T))
sqrt (var (splash_mountain$SPOSTMIN [which (splash_mountain$SPOSTMIN>-999)],na.rm=T))
```
The results of running the R code is 43.3892 for the mean and 31.74894 for the standard deviation. The value looks reasonable now and seems to have fixed our problem.

### Question 4

```{r}
names(splash_mountain)
which(names(splash_mountain) == "SACTMIN")
names(splash_mountain)[3] <- "actual_wait_time"

names(splash_mountain)
which(names(splash_mountain) == "SPOSTMIN")
names(splash_mountain)[4] <- "posted_min_wait_time"
```
The output from executing names(splash_mountain) is: [1] "date"     "datetime" "SACTMIN"  "SPOSTMIN".

### Question 5

```{r}
?as.Date
as.Date(head(splash_mountain$date),"%m/%d/%Y")

myresults <- cut(as.Date(splash_mountain$date, "%m/%d/%Y"), "quarter")
nlevels(myresults)

levels(myresults) <- paste0("q",1:nlevels(myresults))
head(myresults)

splash_mountain$quarters <- myresults
head(splash_mountain)
tail(splash_mountain)
```
There are 20 quarters in the new quarter column.

### Question 6

I acknowledge that the STAT 19000/29000/39000 1-credit Data Mine seminar will be recorded and posted on Piazza, for participants in this course.

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
