---
title: "Project 7 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Katie Brinkers guided with problems 1-7, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
books <- read.csv("/class/datamine/data/goodreads/csv/goodreads_books.csv")
authors <- read.csv("/class/datamine/data/goodreads/csv/goodreads_book_authors.csv")
#Shows number of rows and columns
dim(books)
dim(authors)
```

### Question 2

```{r}
#Breaks books into 4 Categories
book_size <- cut(books$num_pages, breaks=c(0,250,500,1000,Inf), labels = c("small","medium","large","huge"), include.lowest = T)
table(book_size)
```

### Question 3

```{r}
#Calculates the mean of each Category
tapply(books$publication_year, book_size, mean, na.rm=T)
tapply(books$average_rating, book_size, mean, na.rm=T)
tapply(books$text_reviews_count, book_size, mean, na.rm=T)
```
The results did actually surprise me because there was not much of a difference between each category.

### Question 4

```{r}
#Created list of 4 dataframes
booksubset <- books[,c("publication_year","average_rating","text_reviews_count")]
books_by_size <- split(booksubset,book_size)
#Apply column means to each of new dataframe
lapply(books_by_size, colMeans, na.rm=T)
```

### Question 5

```{r}
#Creates an equivalent data frame of my own, by using the subset function
res <- subset(books, subset=language_code %in% c("en-US", "en-CA", "en-GB", "eng", "en", "en-IN") & publication_year > 2000, select=c("author_id", "book_id", "average_rating", "description", "title", "ratings_count", "language_code", "publication_year"))

en_books <- books[books$language_code %in% c("en-US", "en-CA", "en-GB", "eng", "en", "en-IN") & books$publication_year > 2000, c("author_id", "book_id", "average_rating", "description", "title", "ratings_count", "language_code", "publication_year")]
dim(en_books)
dim(res)
```
The differnece is that the subset function removes the NA rows while the other one does not.

### Question 6

```{r}
#Combines res and authors in a way which appends all information from author when there is a match in res
mymergedDF <- merge(res, authors, by="author_id")
dim(mymergedDF)
```

### Question 7

```{r}
#Prints authors and looks into author's highest rated book after declaring an author
abigail <- mymergedDF[mymergedDF$name == "Abigail Thomas",]
abigail[which.max(abigail$ratings_count.x),]$title
```
I agree the book to be the highest rated book from the author because I personally have read that book and enjoyed it very much. I also looked up reviews on Google as well.

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
