---
title: "Project 6 Solutions"
output:
  pdf_document: default
---

```{r, include=F}
# Run this code chunk first to activate the course Python environment.
# Do not remove this. It will not show up in your compiled PDF.
datamine_py()

# Install packages if not already installed.
list.of.packages <- c("knitr")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Remove ## from output.
library(knitr)
opts_chunk$set(comment = NA)
```

## Kevin Choe

## Collaborators: N/A
## TA help: Hilda Ibriga and Katie Brinkers guided with problems 1-5, explained new concepts
## Online resources used: Stat 190 Example Book (All problems)

### Question 1

```{r}
dat <- read.csv("/class/datamine/data/fars/7581.csv")

#Calculates mean number of motorists
tapply(dat$PERSON, dat$DRUNK_DR, mean)

# Read in data that maps state codes to state names
state_names <- read.csv("/class/datamine/data/fars/states.csv")

# Create a vector of state names called v
v <- state_names$state

# Set the names of the new vector to the codes
names(v) <- state_names$code

# Create a new column in the dat dataframe with the actual names of the states
dat$mystates <- v[as.character(dat$STATE)]
```
I prefer to use the tapply function because it is easier and simpler to write.

### Question 2

```{r}
#Sorts states by highest average number of drunk drivers per accident

tapply(dat$DRUNK_DR, dat$mystates, mean)
sort(tapply(dat$DRUNK_DR, dat$mystates, mean), decreasing = TRUE)
```
New Hampshire has the highest average number of drunk drivers per accident.

### Question 3

```{r}
#Sorts total number of fatalities for each day of the week.

sort(tapply(dat$FATALS, dat$DAY_WEEK, sum), decreasing = TRUE)

#Sorts proportion of fatalities over the total number of people in the accidents

sort(tapply(dat$FATALS, dat$DAY_WEEK, sum), decreasing = TRUE)/sort(tapply(dat$PERSONS, dat$DAY_WEEK, sum), decreasing = TRUE)
```
The numbers are suprising to me because Sundays, Saturdays, and Fridays have the highest number of fatalities compared to other days.

I was expecting a smaller proportion for the days with higher number of fatalities. I was expecting a high proportion on day 5.

### Question 4

```{r}
#Sorts average number of crashes involving drunk drivers that occur on straight, curvy, and unknown roads.

sort(tapply(dat$DRUNK_DR, dat$ALIGNMNT, mean), decreasing = TRUE)
```
The average for straight roads is 0.31 and the average for curvy roads is 0.47

### Question 5

```{r}
#Finds the total number of fatalities in time interval

tapply ( dat$FATALS, cut(dat$HOUR, breaks=c(0,6,12,18,24,99), include.lowest=T), sum )

#Finds the average number of fatalities in time interval

tapply ( dat$FATALS, cut(dat$HOUR, breaks=c(0,6,12,18,24,99), include.lowest=T), mean)
```

## Pledge

By submitting this work I hereby pledge that this is my own, personal work. I've acknowledged in the designated place at the top of this file all sources that I used to complete said work, including but not limited to: online resources, books, and electronic communications. I've noted all collaboration with fellow students and/or TA's. I did not copy or plagiarize another's work.

> As a Boilermaker pursuing academic excellence, I pledge to be honest and true in all that I do. Accountable together - We are Purdue.
